A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-11-21 5_generalization.tex
widening figures
extend widening to handle min bead width

\paragraph{Widening}
Complementary to any of these schemes we can enforce a minimum feature size at no extra cost in our framework.
Regions where the model is narrower than the nozzle size can be printed with a bead width larger than the model thickness.
We can simply override
\begin{align*}
W'(n,r)_0 &=
\begin{cases}
\max \left( w^*  ,  W(n,r)_0 \right) & \text{ if } n = 1 \\
W(n,r)_0 & \text{ otherwise}
\end{cases}
\end{align*}

>>>>

\paragraph{Widening}
Complementary to any of these schemes we can enforce a minimum feature size at no extra cost in our framework.
Regions where the model is narrower than some $r_\text{min}$ can be printed with a bead width $w_\text{min}$ larger than the model thickness.
In order to get results such as in \cref{widening} we can override
\begin{align*}
q'(d) &= 
\begin{cases}
0 & \text{ if } 0 \leq d < 2 r_\text{min} \\
1 & \text{ if }  2 r_\text{min} \leq d < w^*  \\
q(d) & \text{ otherwise}
\end{cases}
\\
W'(n,r)_0 &=
\begin{cases}
\max \left( w_\text{min}  ,  2 r \right) & \text{ if } 2 r < w^* \\
W(n,r)_0 & \text{ otherwise}
\end{cases}
\end{align*}

\begin{figure}
\centering
\setlength{\figwidth}{.45\columnwidth}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[width=\columnwidth]{sources-validation-wedge-TEST-Distributed-feature-size.png}
\caption{$w_\text{min} = 2 r_\text{min} = 0.1$ (Distributed)}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[width=\columnwidth]{sources-validation-wedge-TEST-Center-widening.png}
\caption{$w_\text{min} = 0.5$, $2 r_\text{min} = 0.2$ (Center)}
\end{subfigure}
\caption{
Widening strategies.
}
\label{widening}
\end{figure}
